### 2017-12-11 submission/supplemental.Rmd
add table s2

colnames(fs_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycles", "Sub-Sample Depth")

@@

**Table S2:**

@@

>>>>

colnames(fs_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycle", "Sub-Sample Depth")

@@

**Table S2: Tukey Post-Hoc Results of Significant HiFi Taq Differences in Fecal Samples**

@@

fs_tukey <- as.data.frame(read_csv("../data/process/tables/fecal_overall_tukey_results.csv")) %>% 
  mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
  rename(padj = `p adj`) %>% 
  mutate(padj = as.numeric(padj)) %>% 
  filter(padj < 0.05) %>% 
  mutate_at(vars(padj), funs(format(., scientific = TRUE, digits = 2, nsmall = 2)))

colnames(fs_tukey) <- c("Difference", "Lower", "Upper", "P Adjusted", "Comparison", "Cycle", "Sub-Sample Depth")

kable(fs_tukey, format = "markdown", align = 'c', padding = 2)
